---
title: "Plotly Graphics"
author: "David P"
date: "10/12/2017"
output: slidy_presentation
---

```{r Setup, echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
library(RCurl)
library(plotly)
```


```{r GetCleanData,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
# Get the data
df <- read.csv(text=getURL('https://raw.githubusercontent.com/NineTenths/data/master/bad-drivers/bad-drivers.csv'))

# Create the column names
cNames <- c('State','FatalCollision','FatalSpeeding','FatalAlchohol','FatalDistracted','FatalFirstAcc','InsPrem','InsLosses')
names(df) <- cNames

# Add state abbreviation
df$code <- state.abb[match(df$State,state.name)]
```

```{r PreparePlot,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

df$hover <- with(df,paste(State,'<br>',"Number",FatalCollision,"Speeding",FatalSpeeding,'<br>',
                          "Alchohol",FatalAlchohol,"Not Distracted",FatalDistracted,'<br>',
                          "First",FatalFirstAcc,'<br>',"Premiums",InsPrem,"Losses",InsLosses))
```

The following interactive map was created using Plotly with data from [fivethirtyeight.com](http://fivethirtyeight.com/). The data for this plot is available on the [fivethirtyeight GitHub](https://github.com/fivethirtyeight/data). 

This plot illustrates the number of fatal automobile collisions per billion miles of road by US state. Hovering over any state will create a pop-up that provides the following additional information:

* Percentage of drivers who were involved in fatal collisions while speeding
* Percentage of drivers who were involved in fatal collisions while alchohol-impared
* Percentage of drivers who were involved in fatal collisions and were not distracted
* Percentage of drivers who were involved in fatal collisions and it was their first accident
* Car insurance premiums ($)
* Losses incurred by insurance companies for collisions per insured driver ($)

```{r CreatePlot,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
p <- plot_geo(df,locationmode='USA-states') %>%
  add_trace(
    z = ~FatalCollision, text = ~hover, locations = ~code,
    color = ~FatalCollision, colors = 'Reds'
  ) %>%
  colorbar(title='Fatalities') %>%
  layout(
    title='Fatal Collisions per Billion Miles by State<br>(Hover for breakdown)',
    geo=g
  )
p
```

